The \project{unRAVE} catalog

### 2016-09-08 article/unrave.tex
Fix caption of Fig 8

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/repeat-visits.pdf}
\caption{The RMS of the test set labels as a function of S/N ratio for repeated stars in the test set.\label{fig:repeat-visits}}
\end{figure*}

>>>>

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/repeat-visits.pdf}
\caption{The RMS deviation of labels for repeated observations in the test set.  The RMS deviation is binned as a function of the S/N ratio of the individual visit spectra.  The
precision flattens out at S/N $\gtrsim 40$~pixel$^{-1}$, where our results become systematics-limited.
\label{fig:repeat-visits}}
\end{figure*}
